%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
  {Software Developer \& UI Lead} % Affiliation/role
  {JoeZoo Inc.} % Organization/group
  {Toronto, ON.} % Location
  {Apr. 2018 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Core team member of a proof-of-learning and assessment web application that I helped scale to 14K+ schools and 5.8M+ users worldwide.}
      \item {Architected the front-end using the Flux pattern and implemented most core features and utilities.}
      \item {Created a team library of complex and reusable React containers and components such as page layouts, lists, data charts, and other widgets.}
      \item {Wrote key back-end API services in Java (Spring + Grails) that included an automated literacy checker, document parser, and interfaces for our providers.}
      \item {Created internal libraries including automated user tracking, error reporting, language translation, scripts, and more.}
      \item {Created an Originality Checker as part of our NLP pipeline to report copied or similar content against a corpus of documents using spaCy in a Flask service.}
      \item {Helped move authentication to the back-end for offline access.}
      \item {Helped create deployment pipelines for each of our environments (dev/staging/production).}
      \item {Trained and mentored new developers and helped establish a positive working culture.}
    \end{cvitems}
  }


  \cventry
    {Junior Software Developer}
    {} % Organization EMPTY
    {} % Location EMPTY
    {Apr. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems}
        \item {Created and maintained some general use containers and components.}
        \item {Cleaned up majority of the front-end technical debt and helped introduce best practices.}
        \item {Kept our NPM packages up to date and helped minimize third-party code reliance.}
      \end{cvitems}
 	  }

  \cventry
    {Distribution Supervisor \& Dispatch} % Affiliation/role
    {Arctic Glacier Canada Inc.} % Organization/group
    {Mississauga, ON.} % Location
    {Nov. 2015 - May 2016} % Date(s)
    {
      \begin{cvitems} 
        \item {Supervising a team of 30+ company drivers, helpers, technicians, and loaders.}
        \item {Dealt with majority of customer service issues.}
      %   \item {Supervising a team of company drivers, technicians, and loaders; responsible for their safety and compliance as defined by the Ministry of Labour/Transportation.}
      %   \item {Creating and reviewing routes daily, support for customer service representatives, and overseeing the ordering and delivery of merchandise freezers.}
      %   \item {Responsible for dealing with a wide variety of customer service issues including inquiries and concerns.}
      %   \item {Other day to day duties reporting to the distribution manager.}
      \end{cvitems}
 	  }


  \cventry
    {Route Delivery Sales}
    {} % Organization EMPTY
    {} % Location EMPTY
    {Jun. 2010 - Nov. 2015} % Date(s)
    {
      \begin{cvitems}
        \item {Delivering daily to a variety of commercial and industrial locations in Ontario.}
        \item {Go-to employee for training new drivers.}
      % \item {Delivering daily to a variety of commercial and industrial locations in and around the GTA.}
      % \item {Interaction with customers, fulfilling orders, and merchandising according to specifications.}
      % \item {Responsible for expensive equipment: commercial truck with air-brakes and refrigerated unit.}
      % \item {Responsible for training new drivers as well as other extra tasks including installing and removing merchandisers, loading and unloading, and customer service.}
      \end{cvitems}
     }
     
%---------------------------------------------------------
\end{cventries}