% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\usepackage{mdframed}
\usepackage{mdframed}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\definecolor{light-gray}{gray}{0.95}
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Ivan Puljak}  & https://puljak.ca \\
Software Developer & https://github.com/ipuljak \\
15 Isabella Street & ivan@puljak.ca \\
Brampton, ON L6X 1P4 & 416-878-4484 \\
\end{tabular*}
\\

\vspace{0.1in}

\begin{mdframed}[backgroundcolor=light-gray]
\textbf{Education}
\end{mdframed}
\begin{itemize}
\item
	\ressubheading{University of Toronto}{Toronto, ON}{Honours Bachelor of Science, Specialist Computer Science }{Sep. 2009 - Jun. 2014}
	\begin{itemize}
		\resitem{Interest in Computational Linguistics \& Natural Language Processing, Algorithms}
	\end{itemize}

\end{itemize}

\begin{mdframed}[backgroundcolor=light-gray]
\textbf{Work Experience}
\end{mdframed}
\begin{itemize}
\item
	\ressubheading{JoeZoo Inc.}{Toronto, ON}{Software Developer \& UI Lead}{Apr. 2017 - Present}
	\begin{itemize}
		\resitem{Full Stack Developer working on a student assessment \& proof-of-learning web application used by 12K+ schools \& 5M+ users worldwide.}
		\resitem{Very high proficiency working with JavaScript \& React, Grails/Groovy.}
		\resitem{Worked on almost all foundational components for functionality \& user feature sets.}
		\resitem{Created an Originality Checker to report copied/similar content in student coursework using Python \& spaCy as a side project.}
		\resitem{Promoted to UI Lead Apr. 2018.}
	\end{itemize}
\item
	\ressubheading{Arctic Glacier Canada Inc.}{Mississauga, ON}{Distribution Supervisor \& Dispatch}{Nov. 2015 - May 2016}
	\begin{itemize}
		\resitem{Supervising a team of company drivers, technicians, and loaders; responsible for their safety and compliance as defined by the Ministry of Labour/Transportation.}
		\resitem{Creating and reviewing routes daily, support for customer service representatives, and overseeing the ordering and delivery of merchandise freezers.}
		\resitem{Responsible for dealing with a wide variety of customer service issues including inquiries and concerns.}
		\resitem{Other day to day duties reporting to the distribution manager.}
	\end{itemize}
\item
	\ressubheading{Arctic Glacier Canada Inc.}{Mississauga, ON}{Route Delivery Sales}{Jun. 2010 - Nov. 2015}
	\begin{itemize}
		\resitem{Delivering daily to a variety of commercial and industrial locations in and around the GTA.}
		\resitem{Interaction with customers, fulfilling orders, and merchandising according to specifications.}
		\resitem{Responsible for expensive equipment: commercial truck with air-brakes and refrigerated unit.}
		\resitem{Responsible for training new drivers as well as other extra tasks including installing \& removing merchandisers, loading \& unloading, and customer service.}
	\end{itemize}
\end{itemize}

\begin{mdframed}[backgroundcolor=light-gray]
\textbf{Volunteer Work}
\end{mdframed}
\begin{itemize}
\item
	\ressubheading{Habitat For Humanity}{Brampton, ON}{Volunteer}{Aug. 2015 - Present}
	\begin{itemize}
		\resitem{Responsible for general labour at the ReStore where all proceeds go to homes built by the Habitat For Humanity.}
		\resitem{Duties including providing service to customers, sorting \& displaying merchandise, maintaining store order and cleanliness, and unloading trucks.}
	\end{itemize}
\item
	\ressubheading{Learning Enrichment Foundation}{Toronto, ON}{Volunteer}{Feb. 2014}
	\begin{itemize}
		\resitem{Volunteered at LEF as part of a joint program with the University of Toronto.}
		\resitem{Performed routine maintenance around the entire building.}
	\end{itemize}
\end{itemize}

\begin{mdframed}[backgroundcolor=light-gray]
\textbf{Projects}
\end{mdframed}
\begin{itemize}
\item
	\ressubheading{Portfolio \& Personal Website}{https://puljak.ca}{Portfolio}{Present}
	\begin{itemize}
		\resitem{My personal website which hosts many of my projects that I have worked on, as well as photos and other information about me.}
		\resitem{Created using React and deployed on AWS.}
	\end{itemize}
\item
	\ressubheading{The Street View Tourist}{https://github.com/ipuljak/street\_view\_tourist}{Full-stack project}{May 2017}
	\begin{itemize}
		\resitem{A project I made which aims to give the user a virtual tourist experience through being able to explore the various Google Street Views of famous landmarks and locations of the world.}
		\resitem{Created using React/nodejs + MongoDB.}
	\end{itemize}
\item
	\ressubheading{Lava Leaper}{Toronto, ON}{Award winning game at the Level Up Showcase}{Apr. 2014}
	\begin{itemize}
		\resitem{Was the lead developer for an indie game project named Lava Leaper.}
		\resitem{One of 4 games out of 60+ to win an award at "Level Up Showcase", an annually held convention in Toronto which exhibits student-made video games from Canadian universities.}
	\end{itemize}
\end{itemize}

\begin{mdframed}[backgroundcolor=light-gray]
\textbf{Skills}
\end{mdframed}

\begin{description}
\item[Spoken Languages:]
Fluent English \& Serbo-Croatian
\item[Programming Languages:]
JavaScript, Python, Java, Go, Bash
\item[Development:]
GNU/Linux, Git, HTML/CSS, React, SQL, MongoDB, spaCy/NLTK
\item[AWS:]
CLI, S3, EC2, Elastic Beanstalk, Elasticsearch, Route 53, CloudFront
\item[Driving:]
Full DMZ license, 11 years driving experience, clean record
\item[Certifications:]
\hfill\break
Ontario Association of Chiefs of Police (2018) \\
First Aid \& CPR/AED C (2019)
\end{description}

\end{document}
